# shiny_crud

## Start the traditional version by cloning this directory.

## Install the following packages
   NB! load devtools to make it easy to install the shinyFeedback package via github.
The install.packages needs only to be done once, whereas the library() functions need to be done every time you open a new R-session.

```{r, eval=FALSE}
install.packages("shiny")
install.packages("DT")
install.packages("DBI")
install.packages("RSQLite")
install.packages("shinyjs")
install.packages("shinycssloaders")
install.packages("shinyWidgets")
install.packages("shinydashboard")
install.packages("lubridate")
install.packages("shinytoastr")
install.packages("dplyr")
install.packages("dbplyr")
install.packages("rsconnect")
install.packages("packrat")
install.packages("config")

install.packages("devtools")
library(devtools)
install_github("merlinoa/shinyFeedback")
```

## Load libraries

```{r}
library(shiny)
library(DT)
library(DBI)
library(RSQLite)
library(shinyjs)
library(shinycssloaders)
library(shinyWidgets)
library(shinydashboard)
library(lubridate)
library(shinytoastr)
library(shinyFeedback)
library(dplyr)
library(dbplyr)

```

## Open ui.R in the traditional/shiny_app folder in Rstudio
  NB! make sure your working directory is set to  "shiny_crud/traditional"


## Press Run App to start the app on your machine.
